Exploratory Analysis

### 2021-11-27 eda-h.Rmd
started with ggpairs

set.seed(445)
library(leaps)
library(ISLR)
library(tidyverse) 
library(knitr)
library(glmnet) # package for lasso and ridge regression
library(pls)
library(ISLR)
library(ggpubr)
library(MASS)
library(splines)
library(gam)
library(tree)
library(randomForest)
library(gbm)
library(caret)

@@

```{r}
train <- read.csv("train.csv")
```

>>>>

set.seed(445)
library(leaps)
library(ISLR)
library(tidyverse) 
library(knitr)
library(glmnet) # package for lasso and ridge regression
library(pls)
library(ISLR)
library(ggpubr)
library(MASS)
library(splines)
library(gam)
library(tree)
library(randomForest)
library(gbm)
library(caret)
library(GGally)

@@

```{r}
train <- read.csv("train.csv")

head(train)

str(train)
```

```{r}
ggpairs(train)
```
